A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-15 paper.tex
Change a term

\section{System Design Thinking}
\label{section:design_thinking}
\subsection{Data subscription-based trading platform players}
There are three major roles, data providers, data consumers and brokers in our proposed architecture.

>>>>

\section{System Design Thinking}
\label{section:design_thinking}
\subsection{Data subscription-based trading platform players}
There are three major participants, data providers, data consumers and brokers in our proposed architecture.
